---
title: "Fun Maths Stuff"
output: html_notebook
---

This notebook is an ever-growing group of fun maths visualizations. Let's start with the Lorenz Butterfly.

## Lorenz Butterfly

First we need the Lorenz equations:

$$\frac{dx}{dt} = \sigma(y-x)$$
$$\frac{dy}{dt} = x(\rho-z)-y$$
$$\frac{dz}{dt} = xy - \beta z$$
Let's setup the parameters and initial state with the classic parameters ($\sigma=10$, $\rho=28$, $\beta=\frac{8}{3}$).
```{r}
parameters <- c(sigma = 10, rho = 28, beta = 8/3)
state <- c(x = 1 , y = 1 , z = 1)
```
Now let's write a function to return the rates of change for a given time.

```{r}
Lorenz <- function(t, state, parameters) {
  with(as.list(c(state, parameters)), {
    dx <- sigma*(y-x)
    dy <- x*(rho-z) - y
    dz <- x*y - beta*z
    
    list(c(dx, dy, dz))
  })
}
```

We want to run the model for 100 days and give outputs at 0.01 daily intervals so we can create our times.

```{r}
times <- seq(0, 100, by = 0.01)
```

Now we can solve.

```{r}
library(deSolve)
out <- as.data.frame(ode(y = state, times = times, func = Lorenz, parms = parameters, method = "euler"))
head(out)
```
So we can plot this now.

```{r}
plot(out$x, out$z, pch=".")
```
Let's try a 3D plot,

```{r}
library(plotly)
plot_ly(x = out$x, y = out$y, z = out$z, type = "scatter3d", mode = "markers", marker = list(size=1))
```
## Mandelbrot Set

Let $z = 0$. The Mandelbrot set $M \subseteq \mathbb{C}$ is the set of numbers $c \in \mathbb{C}$ such that
$$z_{n+1} = z_n^2 + c$$
remains bounded for all $n \in \mathbb{N}.$

It can be shown that if at any point $|z| > 2$ then $c \notin M$ as M is compact. Hence we only need to check for $|c| \leq 2$.

```{r}
n <- 150

pixels <- matrix(nrow=0, ncol=2)
for (i in -n:n) {
  for (j in -n:n) {
    x = (i/n) * 2
    y = (j/n) * 2
    pixels <- rbind(pixels, c(x, y))
  }
}


A <- matrix(nrow=0, ncol=3)
```

Let $z_n = x_n + iy_n$ and $c = x_c +iy_c$. Then

$$ x_{n+1} = Re(z_n^2 + c) = x_n^2 - y_n^2 + x_c $$
and

$$ y_{n+1} = Im(z_n^2 + c) = 2x_ny_n + y_c. $$


```{r}
max.iteration <- 1000
for (i in 1:((2*n)+1)^2) {
  x <- y <- 0
  iteration <- 0
  while (x^2 + y^2 <= 4 & iteration < 1000) {
    xtemp <- x^2 - y^2 + pixels[i,1]
    y <- 2*x*y + pixels[i,2]
    x <- xtemp
    iteration <- iteration + 1
  }
  A <- rbind(A, c(pixels[i,], iteration))
}
M <- A[A[,3] == max.iteration,]
plot(M[,1], M[,2], pch=".", cex=2)
```
```{r}
plot_ly(x = A[,1], y = A[,2], type = "scatter", mode = "markers", marker = list(size=3), color=A[,3])
```

